---
weight: 15
title: Badges
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
source("hooks.R")
```

# Badges

Get packages based checks to display in your package README for instance.

## Summary badges

Get badge for CRAN checks summary by package name.

`GET [/badges/summary/{package_name}]`

![Badges example, summary for the rhub package](https://cranchecks.info/badges/summary/rhub)

```{r results="asis"}
args <- c("https://cranchecks.info/badges/summary/rhub")
get_and_show(args)
```

## "Worst" badges

Get badge for CRAN checks worst result by package name. :cold_sweat:

`GET [/badges/worst/{package_name}]`

![Badges example, worst for the stringi package](https://cranchecks.info/badges/worst/stringi)

```{r results="asis"}
args <- c("https://cranchecks.info/badges/worst/stringi")
get_and_show(args)
```

## Flavor badges

Get badge for summary of CRAN checks by flavor and package name.

`GET [/badges/flavor/{flavor}/{package}]`

[List of platforms/flavors](https://cran.r-project.org/web/checks/check_flavors.html)

![Badges example, worst for the stringi package](https://cranchecks.info/badges/flavor/r-devel-linux-x86_64-debian-clang/rhub)

```{r results="asis"}
args <- c("https://cranchecks.info/badges/flavor/r-devel-linux-x86_64-debian-clang/rhub")
get_and_show(args)
```
