---
weight: 15
title: Badges
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
source("hooks.R")
```

# Badges

Get packages based checks to display in your package README for instance.

In a Markdown-based README to add a badge you just need something like `![alt text](https://cranchecks.info/badges/summary/{package})`. 

You might want the badge to point at either the CRAN results page or the CRAN checks API page i.e. either

`[![Worst CRAN checks result for the rhub package](https://cranchecks.info/badges/worst/rhub)](https://cran.r-project.org/web/checks/check_results_rhub.html)` to obtain [![Badges example, worst for the rhub package](https://cranchecks.info/badges/worst/rhub)](https://cran.r-project.org/web/checks/check_results_rhub.html).

or

`[![Worst CRAN checks result for the rhub package](https://cranchecks.info/badges/worst/rhub)](https://cranchecks.info/pkgs/rhub)` to obtain [![Badges example, worst for the rhub package](https://cranchecks.info/badges/worst/rhub)](https://cranchecks.info/pkgs/rhub).

## Summary badges

Get badge for CRAN checks summary by package name.

`GET [/badges/summary/{package_name}]`

`[![Summary of CRAN checks results for the rhub package](https://cranchecks.info/badges/summary/rhub)](https://cranchecks.info/pkgs/rhub)` gives [![Summary of CRAN checks results for the rhub package](https://cranchecks.info/badges/summary/rhub)](https://cranchecks.info/pkgs/rhub).

```{r results="asis"}
args <- c("https://cranchecks.info/badges/summary/rhub")
get_and_show(args)
```

## Worst badges

Get badge for CRAN checks worst result by package name. :cold_sweat:

`GET [/badges/worst/{package_name}]`

`[![Worst CRAN checks results for the rhub package](https://cranchecks.info/badges/summary/rhub)](https://cranchecks.info/pkgs/rhub)` gives ![Worst CRAN checks results for the rhub package](https://cranchecks.info/badges/worst/rhub).



```{r results="asis"}
args <- c("https://cranchecks.info/badges/worst/rhub")
get_and_show(args)
```

## Flavor badges

Get badge for summary of CRAN checks by flavor and package name.

`GET [/badges/flavor/{flavor}/{package}]`

:bulb: [List of platforms/flavors](https://cran.r-project.org/web/checks/check_flavors.html)

`[![CRAN checks result on r-devel-linux-x86_64-debian-clang for the rhub package](https://cranchecks.info/badges/flavor/r-devel-linux-x86_64-debian-clang/rhub)](https://cranchecks.info/pkgs/rhub)` gives [![CRAN checks result on r-devel-linux-x86_64-debian-clang for the rhub package](https://cranchecks.info/badges/flavor/r-devel-linux-x86_64-debian-clang/rhub)](https://cranchecks.info/pkgs/rhub).

```{r results="asis"}
args <- c("https://cranchecks.info/badges/flavor/r-devel-linux-x86_64-debian-clang/rhub")
get_and_show(args)
```
