---
weight: 20
title: History
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
source("hooks.R")
```

# History

The `/history/:date` route allows GET requests only. The route is intended for fetching compressed new-line delimited JSON for an individual date, where all CRAN checks data across all packages is combined.

Parameter:

`:date`
: should be of the form `YYYY-MM-DD`

A request to `/history/:date` leads to a redirect (http status 302) and a returned JSON body with a message telling the user to follow the link in the `Location` response header in case they aren't familiar with redirects. The link to follow is a temporary Amazon S3 link to the JSON file for the given date. 

One can automatically get the link to the JSON file by following the redirect. You can do this in curl with the `-L` flag, or in R by using the `followlocation` curl option like `followlocation=1`. 

An important note is the data in the JSON file is NOT valid JSON as an entire entity. Each line of the file IS valid JSON; called newline delimited JSON ([NDJSON](http://ndjson.org/)). You don't have to worry about these details if you use `cchecks::cch_history()`, which takes care of downloading the file and reading in the compressed NDJSON. On the command line, you can do e.g, download the file, save to a `.json.gz` gzip-compressed file extension, then in the next line decompress the file with `gzip`, then pipe to `jq`, and use `head` to get the first 10 lines

```{bash}
curl -vL https://cranchecks.info/history/2020-04-01 > 2020-04-01.json.gz
gzip -dc 2020-04-01.json.gz | jq . | head -n 2
```

:warning: :bulb: For historical data _by package_ refer to the [package history endpoint](#packages-by-name-history).

```{r history, cache=TRUE}
cchecks::cch_history("2020-04-01")
```

```{r, include=FALSE}
file.remove("2020-04-01.json.gz")
```