---
weight: 22
title: Notifications
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
source("hooks.R")
```

# Notifications

## Notifications token

Get a token for CRAN checks notifications.

[Function of the `cchecks` R package: `cchn_register()`](https://docs.ropensci.org/cchecks/reference/cchn_register.html).

`GET [/notifications/token]`

Parameter:

email
: email address

The token is sent by email, not returned via the response body or headers!

```{r results="asis", cache=TRUE}
args <- c("https://cranchecks.info/notifications/token?email=msmaellesalmon@gmail.com")
get_and_show(args)
```

```r
cchecks::cchn_register(email = "jane.doe@cranchecksapidocs.com")
```

## Notifications rules

_This section is not about an endpoint, it is information useful for all notifications endpoint. :nerd:_

:warning: All components of a rule (e.g., status or time) are combined with 'AND'. That is,
if `status="warn"` and `time=3`, the rule is "triggered" only if both
of `status="warn"` and `time=3` components match the cran checks data.

:bulb: If you want achieve 'OR' behavior make multiple rules.

Each rule can have 1 to 4 parameters:

status (str)
: match against check status. one of: ok, note, warn, error, fail

time (int)
: days in a row the match occurs. an integer. can only go 30 days
  back (history cleaned up after 30 days)

platforms (str/int)
: platform the status occurs on, including negation (e.g., "-solaris"). options:
  solaris, osx, linux, windows, devel, release, patched, oldrel

regex (str)
: a regex to match against the text of an error in check_details.output

Examples in words, and their equivalents as a [Ruby hash](https://ruby-doc.org/core-2.7.0/Hash.html)

ERROR for 3 days in a row across 2 or more platforms
: `{'status' => 'error', 'time' => 3, 'platforms' => 2, 'regex' => nil}`

ERROR for 2 days in a row on all osx platforms
: `{'status' => 'error', 'time' => 2, 'platforms' => "osx", 'regex' => nil}`

ERROR for 2 days in a row on all release R versions
: `{'status' => 'error', 'time' => 2, 'platforms' => "release", 'regex' => nil}`

WARN for 4 days in a row on any platform except Solaris
: `{'status' => 'warn', 'time' => 4, 'platforms' => "-solaris", 'regex' => nil}`
    
WARN for 2 days in a row across 9 or more platforms
: `{'status' => 'warn', 'time' => 2, 'platforms' => 10, 'regex' => nil}`

NOTE across all osx platforms
: `{'status' => 'note', 'time' => nil, 'platforms' => "osx", 'regex' => nil}`

NOTE
: `{'status' => 'note', 'time' => nil, 'platforms' => nil, 'regex' => nil}`

error details contain regex 'install'
: `{'status' => nil, 'time' => nil, 'platforms' => nil, 'regex' => "install"}`


## Notifications list

List your notifications rules

[Function of the `cchecks` R package: `cchn_pkg_rule_list()`](https://docs.ropensci.org/cchecks/reference/cchn_rules.html).

`GET [/notifications/rules]`

## Notifications get

List a single notifications rule by its id

`GET [/notifications/rules/{id}]`

[Function of the `cchecks` R package: `cchn_rule_get()`](https://docs.ropensci.org/cchecks/reference/cchn_rules.html).

## Notifications create

Create one or more notifications rules

[Function of the `cchecks` R package: `cchn_rule_add()`](https://docs.ropensci.org/cchecks/reference/cchn_rules.html).

`POST [/notifications/rules]`

### Notifications delete

Delete a single notifications rule by its id

[Function of the `cchecks` R package: `cchn_rule_delete()`](https://docs.ropensci.org/cchecks/reference/cchn_rules.html).


`DELETE [/notifications/rules/{id}]`

