---
weight: 12
title: Packages
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
source("hooks.R")
```

# Packages

Get packages based checks.

[Function of the `cchecks` R package: `cch_pkgs()`](https://docs.ropensci.org/cchecks/reference/cch_pkgs.html).


## Packages

Get checks data for all packages.

`GET [/pkgs]`
Default [limit](#pagination) of 10, max of 1000. 

> Example with [custom offset and limit](#pagination).

```{r results="asis"}
args <- c("https://cranchecks.info/pkgs/?offset=5&limit=2")
get_and_show(args)
```

```{r}
cchecks::cch_pkgs(
  limit = 2, 
  offset = 5
  )
```

## Packages by name

Get checks summary by package name.

[Function of the `cchecks` package: `cch_pkgs_history()`](https://docs.ropensci.org/cchecks/reference/cch_pkgs_history.html)

`GET [/pkgs/{package}]`

```{r results="asis"}
args <- c("https://cranchecks.info/pkgs/rhub")
get_and_show(args)
```

```{r}
cchecks::cch_pkgs(x = "rhub")
```

## Packages by name (history)

Get checks history by package name.

`GET [/pkgs]`
Default [limit](#pagination) of 10, max of 50.

`GET [/pkgs/{package}/history]`

```{r results="asis"}
args <- c("https://cranchecks.info/pkgs/rhub/history")
get_and_show(args)
```

```{r}
cchecks::cch_pkgs_history(x = "rhub")
```

For historical data _across packages_ see the [history endpoint](#history).