---
weight: 10
title: Responses
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
source("hooks.R")
```

# Response codes

For this section of the docs, examples of (bad) requests are given in the Shell tab on the right, and the headers are in the Headers tab.

## 200 (OK) 

Request good!

```{r results="asis"}
args <- c("https://cranchecks.info/heartbeat")
get_and_show(args)
```

## 302 (Found) 

The root `/`, redirects to `/heartbeat`, and `/docs` redirects to what you're reading right now.

```{r results="asis"}
args <- c("https://cranchecks.info/")
get_and_show(args)
```

## 400 (Bad request)

When you have a malformed request, fix it and try again

```{r results="asis"}
args <- c("https://cranchecks.info/maintainers/blablabla")
get_and_show(args)
```

## 404 (Not found) 

When you request a route that does not exist, fix it and try again.
E.g. in the example here we misspell "maintainers" to "maintainer". :see_no_evil:

```{r results="asis"}
args <- c("https://cranchecks.info/maintainer")
get_and_show(args)
```

## 405 (Method not allowed)

When you use a prohibited HTTP method for a given route.
Don't do that. :wink:

```{r results="asis"}
args <- c("-XDELETE", "https://cranchecks.info/pkgs/ropenaq/")
get_and_show(args)
```


## 500 (Internal server error) 

Server got itself in trouble :scream: :sob:; [get in touch with us](https://github.com/ropenscilabs/cchecksapi/issues).

```yaml
HTTP/2 500
date: Thu, 21 May 2020 16:53:33 GMT
content-type: text/html; charset=utf-8
content-length: 0
```
